### 2019-09-12 2019_neurips_vigil/experiments.tex
minor clean up

On the other side we trained SAMNet using IBM's Mi-Prometheus, a framework based on Pytorch. We trained all our models using NVIDIA’s GeForce GTX TITAN X GPUs. We trained  SAMNet for 6 epochs using 8 reasoning steps SAMCells and a hidden state size of 128. The external memory has 128-bit slots.

@@

The first approach is to train a model on the hard training set only and test it on the hard test set. It is the same approach used by the original COG paper ~\cite{yang2018dataset} to evaluate performance on the hard dataset. We achieve a test accuracy of 91.9 \% which represents a 12\% improvement from the COG model score (see Table 2).
It shows that SAMNet's design choices make a difference when it come to harder tasks with longer sequences and more objects to remember.

The second approach is to see if we can generalize from easy to hard setting. We train a model on the canonical dataset and test it on the hard dataset. Doing so we can achieve comparable results than the first approach. It shows that SAMNet has good generalizations abilities. It can adapt well to different sequence lengths and number of distractors.

Finally we train a model on the canonical data set, fine-tune it on the hard data set during only 25k iterations and test it on the hard data set. Thanks to fine-tuning, we can observe a significant improvement from 91.6\%  to 96.5\% test accuracy which represent the state of the art accuracy for the hard setting (classification tasks).
After a short fine-tuning process, the model can generalize well to harder tasks and even surpass the accuracy obtained in the first approach. We note that the third approach is two time faster than the first one and more effective.

>>>>

On the other side we trained SAMNet using IBM's Mi-Prometheus~\cite{kornuta2018acceleratingo}, a framework for research based on Pytorch. We trained all our models using NVIDIA’s GeForce GTX TITAN X GPUs. We trained  SAMNet for 6 epochs using 8 reasoning steps SAMCells and a hidden state size of 128. The external memory has 128-bit slots.

@@

The first approach is to train a model on the hard training set only and test it on the hard test set. It is the same approach used by the original COG paper ~\cite{yang2018dataset} to evaluate performance on the hard dataset. We achieve a test accuracy of 91.9 \% which represents a 12\% improvement from the COG model score (see Table 2).
It shows that SAMNet's design choices make a difference when it come to harder tasks with longer sequences and more distractors objects.

The second approach is to see if we can generalize from the easy to the hard setting. We train a model on the canonical dataset and test it on the hard dataset. Doing so we can achieve comparable results than the first approach. It shows that SAMNet has good generalizations abilities. It can adapt well to different sequence lengths and number of distractors.

Finally we train a model on the canonical data set, fine-tune it on the hard data set during only 25k iterations and test it on the hard dataset. Thanks to fine-tuning, we can observe a significant improvement from 91.6\%  to 96.5\% test accuracy which represents the state of the art accuracy for the hard setting (classification tasks).
After a short fine-tuning process, the model can generalize well to harder tasks and even surpass the accuracy obtained in the first approach. We note that the third approach is two time faster than the first one and more effective.
